% ============================================================================
% Abstract
% ============================================================================
\chapter*{Abstract}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Abstract}

% English Abstract
\noindent
\textbf{VerSimUX: A Grounded Multi-Agent Architecture for Automated Usability Evaluation and Code-Level Remediation of Web Interfaces}

\vspace{1em}

Most automated accessibility tools stop at diagnosis. They flag violations but leave developers to figure out what to change in the code, and no one checks whether the fix actually works. This thesis presents \versimux{}, a multi-agent system we built to close that loop: it detects usability and accessibility issues by simulating diverse user personas in real browser sessions, generates concrete HTML, CSS, and JavaScript patches, and then verifies whether those patches genuinely resolve the problems they target.

At the core of the system is a LangGraph state-graph pipeline that coordinates four agent roles. A supervisor powered by GPT-5.4 analyses the page structure, generates persona profiles, and---after patches are applied---re-evaluates the result to confirm that original issues are resolved. Persona agents, running on Deepseek-v4-pro, navigate the interface through a six-phase cognitive loop (perceive, plan, decide, execute, evaluate, reflect) with five Python-enforced grounding guards that prevent hallucinated actions. Recommender and conflict resolver agents, both running on Opus~4.6, translate clustered issue reports into typed patch proposals and mediate overlapping fixes through multi-round negotiation.

Several design choices proved critical during development. We maintain all agent working memory in Python dataclasses rather than in the LLM context window, which eliminated the state drift and self-contradiction problems we observed in early prototypes. A rule-based trace verifier discards interaction traces where too many steps target non-existent elements, preventing hallucinated findings from reaching downstream analysis. Issue clustering uses HDBSCAN with sentence-transformer embeddings, and a closed-loop correction mechanism re-simulates failing personas on the patched HTML for up to four iterations.

We evaluated the system on 45 HTML pages spanning login forms, dashboards, multi-step wizards, and checkout flows. \versimux{} achieved $F_1$-scores of 0.88 under ISO~9241-110 and 0.94 under Nielsen's heuristics---7 and 10 points above a single-agent baseline, respectively. Persona inconsistency and hallucination rates dropped from 45\% in the baseline to below 1\%. Of the generated patches, 78\% applied successfully and 85\% passed verification, with a 7\% regression rate. In a blind comparison with 12 frontend developers, \versimux{} reports received higher trust ratings (median 5/7 vs.\ 4/7), lower cognitive workload (NASA-TLX 35 vs.\ 50), and a 65\% recommendation acceptance rate compared to 45\% for the baseline.

\vspace{1em}
\noindent\textbf{Keywords:} multi-agent systems, usability evaluation, accessibility testing, automated program repair, LLM grounding, persona simulation, browser automation, patch synthesis



% Optional: Abstract in another language
% \chapter*{Résumé}
% \addcontentsline{toc}{chapter}{Résumé}
% [French/German/Arabic abstract here]
% \newpage
