% ============================================================================
% Acknowledgments
% ============================================================================
\chapter*{Acknowledgments}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgments}

First and foremost, I would like to express my deepest gratitude to my school supervisor, \textbf{Mrs. Farah Barika Ktata}, for her invaluable guidance, patience, and continuous support throughout the duration of this project. Her academic insights and rigorous feedback were fundamental in shaping the technical and theoretical foundations of this thesis.

I am also sincerely grateful to my company supervisors at \textbf{Artibedded}, \textbf{Mr. Makram Zaoui} and \textbf{Mr. Hamza Zgolli}. Their professional expertise, practical advice, and the trust they placed in me allowed me to explore the complexities of multi-agent systems in a real-world engineering context. The collaborative environment they fostered was essential to the successful implementation of the VerSimUX architecture.

My gratitude extends to the faculty members of the \textbf{Higher Institute of Applied Sciences and Technology of Sousse (ISSAT Sousse)}, especially those within the Department of Computer Science, for providing the intellectual framework and resources necessary to complete my Master's studies.

On a personal note, I would like to thank my family and friends for their unwavering encouragement and belief in me. Their support provided the motivation needed to navigate the challenges of this research.

Finally, I would like to thank everyone who contributed, directly or indirectly, to the realization of this work.
